Sufficient Conditions for Reachability in Automata Networks with Priorities

### 2015-02-12 parts/def-ph.tex
sect 3

\begin{definition}[Asynchronous Automata Networks]
\label{def:ph}
  An \emph{Asynchronous Automata Network} (AAN) is a triplet $\PH = (\PHs; \PHl; \PHa)$,
  where:
  \begin{itemize}
    \item $\PHs \DEF \{a, b, \dots, z\}$ is the finite set of \emph{automata};
    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of
      (global) \emph{states},
      where $\PHl_a = \{a_0, \ldots, a_{l_a}\}$ is the finite set of \emph{local states}
      of automaton $a \in \PHs$, with $l_a \in \sN^*$,
      and so that:
      $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$;
    \item $\PHa \DEF \{\PHfrappe{A}{b_j}{b_k} \mid
      b \in \PHs \wedge (b_j; b_k) \in \PHl_b \times \PHl_b \wedge
      b_j \neq b_k \wedge
      \forall a \in \PHs, \card{A \cap \PHl_a} \leq 1 \wedge
      A \cap \PHl_b = \emptyset \}$ is the finite set of \emph{actions}.
  \end{itemize}
  Furthermore,
  we call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all local states in the model.
\end{definition}
%
\noindent
The automaton that a local state $a_i$ belongs to is referred to as $\PHsort(a_i) = a$.
Given a state $s\in \PHl$, the local state of automaton $a \in \PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is, the $a$-coordinate of the state $s$.
If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.
\pref{def:substate} defines the notion of sub-state on a set of automata, that is used to focus on the interesting part of a complete state.
We note that a state is \textit{a fortiori} a sub-state.
The override of a state $s$ by a local state $a_i$ (or by a set of local states)
is defined in \pref{def:statecap} as the same state in which the local state of automaton $a$ has been replaced by $a_i$;
this is used to define the semantics of an AAN in \pref{def:play}.
%
\begin{definition}[Sub-states ($\PHsublize{\PHl}$)]
\label{def:substate}
  If $S \subseteq \PHs$ is a set of automata, a sub-state on $S$ is an element of:
  $\PHsubl[\PHl]_S \DEF \bigtimes{a \in S} \PHl_a$.
  The set of all sub-states is:
  $\PHsubl[\PHl] \DEF \bigcup_{S \in\powerset(\PHs)} \PHsubl[\PHl]_S$.

@@

\begin{example}
  \pref{fig:ph-livelock} gives an example of AAN where:
  \begin{align*}
    \PHs &= \{ a, b, c \} \enspace,
      & \PHl_a &= \{ a_0, a_1 \} \enspace, \\
    \PHl_b &= \{ b_0, b_1 \} \enspace,
      & \PHl_c &= \{ c_0, c_1 \} \enspace, \\
    \PHh = \{ \quad
      & \PHfrappem{a_1}{a_0} \enspace , \quad
        \PHfrappem{a_0}{a_1} \enspace , \\
      & \PHfrappem{b_1}{b_0} \enspace , \quad
        \PHfrappem{b_0}{b_1} \enspace , \\
      & \PHfrappes{a_1, b_1}{c_0}{c_1} \enspace \quad \qquad \qquad
      \quad \}
  \end{align*}

@@

Finally, we define the support (\pref{def:supp}) of a sequence of actions $\zeta$
as the set containing the first local state of each automata appearing in $\zeta$,
that is, as a hitter or as a target.
For this, we first define the \emph{first appearance} of an automata
in this sequence.

>>>>

\begin{definition}[Asynchronous Automata Networks]
\label{def:ph}
  An \emph{Asynchronous Automata Network} (AAN) is a triplet $\PH = (\PHs; \PHl; \PHa)$,
  where:
  \begin{itemize}
    \item $\PHs \DEF \{a, b, \dots, z\}$ is the finite set of \emph{automata};
    \item $\PHl \DEF \underset{a \in \PHs}{\times} \PHl_a$ is the finite set of
      (global) \emph{states},
      where $\PHl_a = \{a_0, \ldots, a_{l_a}\}$ is the finite set of \emph{local states}
      of automaton $a \in \PHs$, with $l_a \in \sN^*$,
      and so that:
      $\forall (a_i; b_j) \in \PHl_a \times \PHl_b, a \neq b \Rightarrow a_i \neq b_j$;
    \item $\PHa \DEF \{\PHfrappe{A}{b_j}{b_k} \mid
      b \in \PHs \wedge (b_j; b_k) \in \PHl_b \times \PHl_b \wedge
      b_j \neq b_k \wedge
      \forall a \in \PHs, \card{A \cap \PHl_a} \leq 1 \wedge
      A \cap \PHl_b = \emptyset \}$ is the finite set of \emph{actions}.
  \end{itemize}
  Furthermore,
  we call $\PHproc \DEF \bigcup_{a \in \PHs} \PHl_a$ the set of all local states in the model.
\end{definition}
%
\noindent
The automaton that a local state $a_i$ belongs to is referred to as $\PHsort(a_i) = a$.
Given a state $s\in \PHl$, the local state of automaton $a \in \PHs$ present in $s$ is denoted by $\PHget{s}{a}$, that is, the $a$-coordinate of the state $s$.
If $a_i \in \PHl_a$, we define the notation $a_i \in s \EQDEF \PHget{s}{a} = a_i$.

\begin{comment}
\pref{def:substate} defines the notion of sub-state on a set of automata, that is used to focus on the interesting part of a complete state.
We note that a state is \textit{a fortiori} a sub-state.
The override of a state $s$ by a local state $a_i$ (or by a set of local states)
is defined in \pref{def:statecap} as the same state in which the local state of automaton $a$ has been replaced by $a_i$;
this is used to define the semantics of an AAN in \pref{def:play}.
%
\begin{definition}[Sub-states ($\PHsublize{\PHl}$)]
\label{def:substate}
  If $S \subseteq \PHs$ is a set of automata, a sub-state on $S$ is an element of:
  $\PHsubl[\PHl]_S \DEF \bigtimes{a \in S} \PHl_a$.
  The set of all sub-states is:
  $\PHsubl[\PHl] \DEF \bigcup_{S \in\powerset(\PHs)} \PHsubl[\PHl]_S$.

@@

\begin{example}
  \pref{fig:ph-livelock} gives an example of AAN where:
  \begin{align*}
    \PHs &= \{ a, b, c \} \enspace,
      & \PHl_a &= \{ a_0, a_1 \} \enspace, \\
    \PHl_b &= \{ b_0, b_1 \} \enspace,
      & \PHl_c &= \{ c_0, c_1 \} \enspace, \\
    \PHh = \{ \quad
      & \PHfrappem{a_1}{a_0} \enspace , \quad
        \PHfrappes{b_0}{a_0}{a_1} \enspace , \\
      & \PHfrappem{b_1}{b_0} \enspace , \quad
        \PHfrappes{a_0}{b_0}{b_1} \enspace , \\
      & \PHfrappes{a_1, b_1}{c_0}{c_1} \enspace \quad \qquad \qquad
      \quad \}
  \end{align*}

@@

\begin{comment}
Finally, we define the support (\pref{def:supp}) of a sequence of actions $\zeta$
as the set containing the first local state of each automata appearing in $\zeta$,
that is, as a hitter or as a target.
For this, we first define the \emph{first appearance} of an automata
in this sequence.

### 2015-02-12 parts/example.tex
minor fixes
sect 3

Finally, the static analysis results presented in
\pref{ssec:ua} and \pref{ssec:ordered-ua} can be used to check if the model is functional,
\ie if gene $a$ can oscillate, thus leading to the formation of stripes.
Starting from context $\ctx = \PHstate{f_1, a_0, c_0}$,
we thus want to check the reachability of
$\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{a_0}{a_1}$.
Rather than checking this whole objective sequence with \pref{th:approxinf},
we break it using \pref{thm:ordered-ua}.
We first build the first saturated graph of local causality
based on the first objective, $\w_1 = \PHobj{a_0}{a_1}$, in the initial context $\ctx$.
This graph is depicted in \pref{fig:metazoan-sa}(left).
%and given \pref{tmh:approxinf}, we have:
We have especially:
\[\allprocs(\thisB{\w_1}{\ctx}) = \{ a_0, c_0, f_1 \} \enspace \text{and}\]
\[\lastprocs(\PHobj{a_0}{a_1}) = \{\{ a_1, c_0, f_1 \}\} \enspace.\]
Therefore, the second step consists of computing the saturated graph of local causality
of the objective $\w_2 = \PHobj{a_1}{a_0}$
in the context
\[\ctx' = \ctx \Cap \allprocs(\thisB{\w_1}{\ctx}) \Cap \lastprocs(\PHobj{a_0}{a_1}) = \PHstate{a_1, c_0, f_1} \enspace.\]
This second graph is given in \pref{fig:metazoan-sa}(middle).
Finally, because
\[\allprocs(\thisB{\w_2}{\ctx'}) = \{ a_1, c_0, c_1, f_1 \} \enspace \text{and}\]
\[\lastprocs(\PHobj{a_1}{a_0}) = \{\{ a_0, c_1 \}\} \enspace,\]
The last step is then checking
the objective $\w_3 = \PHobj{a_0}{a_1}$
in the context
\[\ctx'' = \ctx' \Cap \allprocs(\thisB{\w_2}{\ctx'}) \Cap \lastprocs(\PHobj{a_1}{a_0}) = \PHstate{a_0, c_1, f_1} \enspace.\]
This last graph is depicted in \pref{fig:metazoan-sa}(right).
In conclusion, by using \pref{thm:ordered-ua} on these saturated graphs of local causality,
we can conclude that the initial objective $\w$ is reachable,
and thus that the AAN of \pref{fig:metazoan-ph} is functional.
This result can be extended to the model of \pref{fig:metazoan-php}
because they have the same dynamics (given \pref{th:bisimPHP}).

@@

    \node[Aproc,below right of=ta01ss] (tc0) {$c_0$};
    \node[Aobj,below of=tc0] (tc10) {$\PHobj{c_1}{c_0}$};
    \node[Asol,below of=tc10] (tc10s) {};
    \node[Aobj,right of=tc10] (tc00) {$\PHobj{c_0}{c_0}$};
    \node[Asol,below of=tc00] (tc00s) {};
    \node[Assol,below of=tc00s] (tnc00s) {$\emptyset$};

    \node[Aproc,below of=tc10s] (ta0) {$a_0$};
    \node[Aobj,below of=ta0] (ta00) {$\PHobj{a_0}{a_0}$};
    \node[Asol,below of=ta00] (ta00s) {};
    \node[Assol,below of=ta00s] (tna00s) {$\emptyset$};

@@

    (tc10s) edge (ta0)
    (ta0) edge (ta00)
    (ta00) edge (ta00s)
    (ta00s) edge (tna00s)
    ;
  \end{tikzpicture}
  \caption{%
  \label{fig:metazoan-sa}%
    The three successive saturated graphs of local causality
    of the AAN in \pref{fig:metazoan-ph}
    for the objective sequence
    $\w = \PHobj{a_0}{a_1} \concat \PHobj{a_1}{a_0} \concat \PHobj{a_0}{a_1}$
    and the initial context
    $\ctx = \PHstate{a_0, c_0, f_1}$.
    The (left) graph allows to check objective $\PHobj{a_0}{a_1}$
    from the initial context $\ctx$.
    The (middle) graph is for the objective $\PHobj{a_1}{a_0}$
    and the context $\PHstate{a_1, c_0, f_1}$.
    The (right) graph is for the last objective, $\PHobj{a_0}{a_1}$,
    and the context $\PHstate{a_0, c_1, f_1}$.
  }
\end{figure}

>>>>

Finally, the static analysis results presented in
\pref{ssec:ua} and \pref{ssec:ordered-ua} can be used to check if the model is functional,
\ie if gene $a$ can oscillate, thus leading to the formation of stripes.
Starting from context $\ctx = \PHstate{f_1, a_0, c_0}$,
we thus want to check the reachability of
$\w = \PHobj{a_0}{a_1} \PHconcat \PHobj{a_1}{a_0} \PHconcat \PHobj{a_0}{a_1}$.
Rather than checking this whole objective sequence with \pref{th:approxinf},
we break it using \pref{ssec:ordered-ua}.
We first build the first saturated graph of local causality
based on the first objective, $\w_1 = \PHobj{a_0}{a_1}$, in the initial context $\ctx$.
This graph is depicted in \pref{fig:metazoan-sa}(left).
%and given \pref{tmh:approxinf}, we have:
We have especially:
\[\allprocs(\thisB{\w_1}{\ctx}) = \{ a_0, c_0, f_1 \} \enspace \text{and}\]
\[\lastprocs(\PHobj{a_0}{a_1}) = \{\{ a_1, c_0, f_1 \}\} \enspace.\]
Therefore, the second step consists of computing the saturated graph of local causality
of the objective $\w_2 = \PHobj{a_1}{a_0}$
in the context
\[\ctx' = \ctx \Cap \allprocs(\thisB{\w_1}{\ctx}) \Cap \lastprocs(\PHobj{a_0}{a_1}) = \PHstate{a_1, c_0, f_1} \enspace.\]
This second graph is given in \pref{fig:metazoan-sa}(middle).
Finally, because
\[\allprocs(\thisB{\w_2}{\ctx'}) = \{ a_1, c_0, c_1, f_1 \} \enspace \text{and}\]
\[\lastprocs(\PHobj{a_1}{a_0}) = \{\{ a_0, c_1 \}\} \enspace,\]
The last step is then checking
the objective $\w_3 = \PHobj{a_0}{a_1}$
in the context
\[\ctx'' = \ctx' \Cap \allprocs(\thisB{\w_2}{\ctx'}) \Cap \lastprocs(\PHobj{a_1}{a_0}) = \PHstate{a_0, c_1, f_1} \enspace.\]
This last graph is depicted in \pref{fig:metazoan-sa}(right).
In conclusion, by following \pref{ssec:ordered-ua} on these saturated graphs of local causality,
we can conclude that the initial objective $\w$ is reachable,
and thus that the AAN of \pref{fig:metazoan-ph} is functional.
This result can be extended to the model of \pref{fig:metazoan-php}
because they have the same dynamics (given \pref{th:bisimPHP}).

@@

    \node[Aproc,below right of=ta01ss] (tc0) {$c_0$};
    \node[Aobj,below of=tc0] (tc10) {$\PHobj{c_1}{c_0}$};
    \node[Asol,below of=tc10] (tc10s) {};
    \node[Assol,below of=tc10s] (tnc10s) {$\{ a_0 \}$};
    \node[Aobj,right of=tc10] (tc00) {$\PHobj{c_0}{c_0}$};
    \node[Asol,below of=tc00] (tc00s) {};
    \node[Assol,below of=tc00s] (tnc00s) {$\emptyset$};

    \node[Aproc,below of=tnc10s] (ta0) {$a_0$};
    \node[Aobj,below of=ta0] (ta00) {$\PHobj{a_0}{a_0}$};
    \node[Asol,below of=ta00] (ta00s) {};
    \node[Assol,below of=ta00s] (tna00s) {$\emptyset$};

@@

    (tc10s) edge (tnc10s)
    (tnc10s) edge (ta0)
    (ta0) edge (ta00)
    (ta00) edge (ta00s)
    (ta00s) edge (tna00s)
    ;
  \end{tikzpicture}
  \caption{%
  \label{fig:metazoan-sa}%
    The three successive saturated graphs of local causality
    of the AAN in \pref{fig:metazoan-ph}
    for the objective sequence
    $\w = \PHobj{a_0}{a_1} \concat \PHobj{a_1}{a_0} \concat \PHobj{a_0}{a_1}$
    and the initial context
    $\ctx = \PHstate{a_0, c_0, f_1}$.
    The (left) graph allows to check objective $\PHobj{a_0}{a_1}$
    from the initial context $\ctx$.
    The (middle) graph is for the objective $\PHobj{a_1}{a_0}$
    and the context $\PHstate{a_1, c_0, f_1}$.
    The (right) graph is for the last objective, $\PHobj{a_0}{a_1}$,
    and the context $\PHstate{a_0, c_1, f_1}$.
  }
\end{figure}

### 2015-02-12 parts/sa.tex
sect 3

Our approach relies on abstractions of scenarios that have been introduced in
\cite{PMR12-MSCS} for the static analysis of reachability in the Process Hitting framework,
a particular sub-class of AAN (see the Remark at the end of the previous section).
In this paper, we generalize the static analysis for the case of the under-approximation of
reachability in any AAN.

\todo{outline}

@@

  We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same automaton, if it exists.
  The set of all objective sequences is denoted by $\OS$.
\end{definition}

We define the partial ordering relation $\ltw$ between two objective sequences (\pref{def:ltw}) as
follows:
$w\ltw w'$ if and only if there exists a mapping between all the objective bounces of $w'$ in $w$
that preserve the sequentiality.

\todo{support compatibility}

\begin{definition}[$\ltw \subset \OS\times\OS$]\label{def:ltw}
$\w\ltw\w'$ if and only if
$|\w|\geq|\w'|$ and
there exists a mapping $\phi: \indexes{\w'}\mapsto \indexes{\w}$ such that
$\forall n,m \in\indexes{\w'}, n<m \Leftrightarrow \phi(n)<\phi(m)$,
and
$\forall n\in\indexes{\w'}, \bounce{\w'_n}=\bounce{\w_{\phi(n)}}$
\end{definition}

@@

An objective sequence can be seen as an abstract representation of a set of scenarios that describe
(part of) the successive state changes of the automata.
We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios concretising an objective sequence
$\w$ in the state $s\in\PHs$.
It is essentially all the scenarios for which there exists a mapping from the bounces of each
objective to the bounce of an action in the scenario which preserve the sequential ordering.

\todo{compatibility of $\w$ with $s$}

\begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
Given $\w\in\OS$, $\concr(\w)$ is the set of scenarios concretising $\w$ in the
state $s$:
\begin{align*}
\concr(\w) \DEF \{ \delta\in\Sce(s)\mid & (\w^\vartriangle=\emptyseq \wedge
\delta=\emptyseq)  \vee (
\w^\vartriangle\neq \emptyseq\wedge
\\ &
 \wedge \exists \phi:\indexes{\w}\mapsto\indexes{\delta},
    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m))
\\ & \qquad
	\wedge \forall n\in\indexes{\w},
	  \bounce{\w_n} \in s\play\delta_{1..\phi(n)})
\}
\enspace,
\end{align*}
where $\omega^\vartriangle$ refers to the objective sequence $\omega$ where
trivial objectives have been removed.
The notation $\delta_{a..b}$ in the previous definition
denotes the subsequence of $\delta$ between indexes $a$ and $b$,
as defined on page \pageref{notations}.
\end{definition}

@@

From \pref{def:bs}, we can derive that any scenario concretising an objective includes all the
actions of one of the bounce sequences of the objective (\pref{lem:bs-concr}).
\begin{lemma}
Given a state $s\in \PHl$ and an objective $\obj{a_i}{a_j}$ with $\get{s}{a}=a_i$,
$\forall\delta\in\concr(\obj{a_i}{a_j})$,
$\exists\zeta\in\BS(\obj{a_i}{a_j})$ such that
$\exists \phi: \indexes{\zeta}\to\indexes{\delta}$
with
$\forall n,m\in\indexes{\zeta}, n<m \Leftrightarrow \phi(n)<\phi(m)$
and
$\forall n\in\indexes{\zeta}$, $\zeta_n = \delta_{\phi(n)}$.
\label{lem:bs-concr}
\end{lemma}

@@

@@

\subsection{Sequential Under-approximation}
\label{ssec:ordered-ua}

In this section, we briefly explain an alternative sufficient condition that
can be applied when looking for scenarios that successively reach a sequence of local states (e.g.,
first reach $a_j$, then later $b_k$, \ldots).

The approach proposed in this sub-section essentially applies the previous under-approximation for
the first local states, and then computes a set of contexts that may be considered as the starting
point for the next local states.
In that way, the local states to reach are taken into account separately, which implies that only a
subset of scenarios can be captured.
%However, because each iteration focuses on a smaller part of the network, this
%sequential under-approximation may be more conclusive.

\todo{computes possible outcomes from the LCG, gives it as context for the next stage}.

\subsection{Reachability of a State}
\label{ssec:simult-ua}

@@

The reachability property studied so far concerns a single local state at a time.
However, we remark that the reachability of a global state or a sub-state can be
addressed with the very same analysis by introducing a dedicated automata.
Such analysis was not possible with the Process Hitting framework,
because of the lack of the notion of simultaneity for more than two components.

In order to check the reachability of a global state $s \in \PHl$,
let $\PH = (\PHs, \PHl, \PHh)$ be an AAN.
We define a new AAN $\PH' = (\PHs', \PHl', \PHh')$ with:
$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
and $\PHh' = \PHh \cup \{ \PHhit{\toset{s}}{\reach_0}{\reach_1} \}$.
Given an initial context $\ctx$, the reachability of $s$ in $\PH$
is equivalent to the concretization of $\PHobjp{\reach}{0}{1}$ in $\PH'$
from the initial context $\ctx \cup \{ \reach_0 \}$,
which can be efficiently under-approximated using \pref{th:approxinf}.

It is of course also possible to compute the reachability
of a sub-state $s \in \PHsubl[\PHl]_S$ of a set of components $S \subseteq \PHs$
with the same method.
One can also check the reachability of a set of states $\Lambda \subseteq \PHl$
by creating several actions
$\PHhit{\toset{s}}{\reach_0}{\reach_1}$ in $\PHh$ for each state $s \in \Lambda$.

>>>>

Our approach relies on abstractions of scenarios (\pref{ssec:abstr-sce}) that have been introduced in
\cite{PMR12-MSCS} for the static analysis of reachability in the Process Hitting framework,
a particular sub-class of AAN (see the Remark at the end of the previous section).
In this paper, we generalize the static analysis for the case of the under-approximation of
reachability in any AAN (\pref{ssec:ua}).

In \pref{ssec:concret}, we detail a procedure to extract a witness scenario
concretizing a given local state reachability property.
Finally, we discuss in \pref{ssec:ordered-ua} how the static analysis can be
extended to sequential (sub)states reachability properties.

@@

  We define an \emph{objective sequence} as a sequence of objectives in which each objective target must be equal to the previous objective bounce of the same automaton, if it exists.
  The set of all objective sequences is denoted by $\OS$.
  Given $\w\in\OS$, $\PHsort(\w) \DEF \{\PHsort(\w_i)\mid i\in\indexes{\w}\}$.
For each automaton $a\in\PHsort(\w)$,  the first local state of $a$ referenced in
$\w$ is denoted by $\first_a(\w) \DEF \target{\w_m}$, where $m=\min\{n\in\indexes{\w}\mid \PHsort(\w)=a\}$.
\end{definition}

We define the partial ordering relation $\ltw$ between two objective sequences (\pref{def:ltw}) as
follows:
$w\ltw w'$ if and only if there exists a mapping between all the objective bounces of $w'$ in $w$
that preserve the sequentiality, provided that each automaton starts in the same
local state.

\begin{definition}[$\ltw \subset \OS\times\OS$]\label{def:ltw}
$\w\ltw\w'$ if and only if
$|\w|\geq|\w'|$,
$\forall a\in\PHsort(\w'), a\in\PHsort(\w) \wedge \first_a(\w')=\first_a(\w)$;
and there exists a mapping $\phi: \indexes{\w'}\mapsto \indexes{\w}$ such that
$\forall n,m \in\indexes{\w'}, n<m \Leftrightarrow \phi(n)<\phi(m)$,
and
$\forall n\in\indexes{\w'}, \bounce{\w'_n}=\bounce{\w_{\phi(n)}}$
\end{definition}

@@

An objective sequence can be seen as an abstract representation of a set of scenarios that describe
(part of) the successive state changes of the automata.
We denote by $\concr(\w)$ (\pref{def:concr}) the set of scenarios matching with an objective sequence
$\w$ in the state $s\in\PHs$.
It is essentially all the scenarios for which there exists a mapping from the bounces of each
objective to the bounce of an action in the scenario which preserve the sequential ordering.

\begin{definition}[$\concr: \OS \to \powerset(\Sce)$]\label{def:concr}
Given a state $s\in\PHl$ and an objective sequence
$\w\in\OS$ such that $\forall a\in\PHsort(\w), \first_a(\w)\in s$,
$\concr(\w)$ is the set of scenarios matching with $\w$:
\begin{align*}
\concr(\w) \DEF \{ \delta\in\Sce(s)\mid & (\w^\vartriangle=\emptyseq \wedge
\delta=\emptyseq)  \vee (
\w^\vartriangle\neq \emptyseq\wedge
\\ &
 \wedge \exists \phi:\indexes{\w}\mapsto\indexes{\delta},
    (\forall n,m\in\indexes{\w}, n<m \Leftrightarrow \phi(n)\leq\phi(m))
\\ & \qquad
	\wedge \forall n\in\indexes{\w},
	  \bounce{\w_n} \in s\play\delta_{1..\phi(n)})
\}
\enspace,
\end{align*}
where $\omega^\vartriangle$ refers to the objective sequence $\omega$ where
trivial objectives have been removed.
The notation $\delta_{a..b}$ in the previous definition
denotes the subsequence of $\delta$ between indexes $a$ and $b$,
as defined on page \pageref{notations}.
\end{definition}

@@

\begin{example}
Given the AAN of \pref{fig:ph-livelock},
$\BS(\obj{c_0}{c_1}) = \{\PHfrappes{a_1,b_1}{c_0}{c_1}\}$;
and 
$\BS(\obj{a_0}{a_1}) = \{\PHfrappes{b_0}{a_0}{a_1}\}$.
\end{example}

From \pref{def:bs}, we can derive that any scenario matching with an objective includes all the
actions of one of the bounce sequences of the objective (\pref{lem:bs-concr}).
\begin{lemma}
Given a state $s\in \PHl$ and an objective $\obj{a_i}{a_j}$ with $\get{s}{a}=a_i$,
$\forall\delta\in\concr(\obj{a_i}{a_j})$,
$\exists\zeta\in\BS(\obj{a_i}{a_j})$ such that
$\exists \phi: \indexes{\zeta}\to\indexes{\delta}$
with
$\forall n,m\in\indexes{\zeta}, n<m \Leftrightarrow \phi(n)<\phi(m)$
and
$\forall n\in\indexes{\zeta}$, $\zeta_n = \delta_{\phi(n)}$.
\label{lem:bs-concr}
\end{lemma}

@@

\todo{the procedure is non-deterministic, make it deterministic? (list all the
scenarios}

@@

\todo{name + prototype of the procedure}

\subsection{Addressing Sequential and Sub-state Reachability}
\label{ssec:ordered-ua}
\label{ssec:simult-ua}

@@

In this section, we briefly discuss how the presented static analysis for local
state reachability properties can be extended to sequential (sub)states
reachability properties.

\paragraph{Sub-state reachability.}
Given an AAN $\PH = (\PHs, \PHl, \PHh)$,
a sub-set of automata local states
$ps = \{ a_i \in\Proc\mid a\in\PHs, a_i\in\PHl(a)\}$,
the reachability from $s\in\PHl$ of a state $s'\in\PHl$ such that
$ps\subset s'$ is equivalent to the reachability of the local state
$\reach_1$ from a state $s\uplus\langle\reach_0\rangle$
in the AAN
$\PH' = (\PHs', \PHl', \PHh')$ with:
$\PHs' = \PHs \cup \{ \reach \}$, $\PHl' = \PHl \times \PHl_\reach$,
where $\PHl_\reach = \{ \reach_0, \reach_1 \}$,
and $\PHh' = \PHh \cup \{ \PHhit{ps}{\reach_0}{\reach_1} \}$.

Such analysis was not possible with the Process Hitting framework,
because of the lack of the notion of simultaneity for more than two components.

\paragraph{Sequential reachability.}
Given a sequence of local state to reach (e.g., reach $a_i$, then $b_j$),
one can use the same approach as for sub-state reachability by introducing
a new automaton $\reach$ having $n+1$ local states where $n$ is the size of the
sequence of reachability and $n$ actions making it bounce from $\reach_0$ to
$\reach_n$ with hitters corresponding the successive local states
(e.g., $\PHfrappes{a_i}{\reach_0}{\reach_1}$ and
$\PHfrappes{b_j}{\reach_0}{\reach_1}$).

An alternative approach is to use the extraction of a scenario of the previous
sub-section:
given the initial state, and a first local state reachability property, one
compute a possible scenario witnessing this reachability.
Then the next local state reachability properties is computed from the
state that outcomes from the latter scenario.
